--- 
title: "Pulp Down"
subtitle: "A Demo Template with CSS for Paged Media"
author: ["Romain Lesur", "R", "RMarkdown", "Bookdown", "Knitr", "Pandoc", "HTML", "CSS", "Prince"]
abstract: |
  ::: {.headline}
  _TeX's Dead_
  :::
  Cover Image by Frank Black Noir [CC BY 2.0](  https://creativecommons.org/licenses/by/2.0), via Wikimedia Commons  
  Advertisement: *Over There*, 1918, by Louis Fancher [Public domain], via Wikimedia Commons
date: "October"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
---

```{r echo=FALSE}
knitr::opts_chunk$set(dev.args = list(bg = NA))
```

# Confession {-}

I gave up. Every time, _It_ has been stronger than me.  

Three times in my life, I painfully tried to control _It_. And there were always these warnings I should have understood!

_It_ is so heavy, sprawling, mysterious and powerful. I knew, though, that if I did not use _It_, I would lose _It_. Actually, this is _It_ that lost me.

I will never try to learn _LaTeX_ anymore, all of that is over. I will always be ilLaTeXerate and I am proud.

I decided to follow a different path that many consider to be far from the utmost respect for the typesetting rules.

I do not care because I have fun.

Now, I am able to develop, with little efforts, this type of utterly useless template! For sure, nobody needs to write a pulp magazine with the **bookdown** package [@R-bookdown]. 

This template is a joke. My main motivation is to make it known that `r fontawesome::fa("r-project", fill="#785963")` users are not tied to LaTeX in order to produce good looking printed books.  

Having read _In HTML and  the Web I Trust_ [@latexisdead], I wanted to make reference to a line from _Pulp Fiction_ [@pulpfiction] uttered by Butch Coolidge: that explains the choice of a pulp magazine.

Believe me, there is a life after LaTeX.


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'weasydoc'
), 'packages.bib')
```

